SDSS-IV MaNGA: The Radial Profile of Enhanced Star Formation in Close Galaxy Pairs

### 2020-10-21 maintex.tex
corrected {\sc } error, use \citealias for paper I

Where $NUV-r$ is the color from SDSS's $k$-corrected absolute magnitude and $\mathcal{M}_i$ is the $i$-band magnitude from the NSA catalog. We further apply an \ewha\ $\ge$ 3\AA\ cut on galaxy spectra extracted from a 1.0~\reff\ aperture to ensure that all passive galaxies are removed from the sample \citep{Cid-Fernandes:2011}. Finally, we use the BPT diagnostic \citep{Baldwin:1981} to remove galaxies with possible AGN in their centers. Specifically, we use the emission line ratios, log([O~\sc{iii}]/H$\beta$) and log([N~\sc{ii}]/H$\alpha$), extracted from a 1.3~kpc aperture along with the maximum starburst line of \citet{Kewley:2001} as the demarcation between the star-forming branch and the AGN branch.

@@

In our previous work, \citet{Fu:2018}, using the 2168 unique galaxies from DR14 \citep{Abolfathi:2018}, we showed that $\sim$5.7\% of the MaNGA observations have at least one companion galaxy within the field of view of the IFU. In this work we use a refined pair identification process which is also expanded for the most recent internal data release, MPL-8.

@@

To select paired galaxies out of our object catalog, we inspect the spectra of each object. We use our own {\sc idl} based spectral fitting code, {\sc spfit}, to model the spectra from the MaNGA datacubes. {\sc spfit} simultaneously fits emission lines and the stellar continuum with the Levenberg-Marquardt nonlinear least-squares minimization algorithm \citep{Fu:2018}. Emission lines are parameterized as a Gauss-Hermite series and the stellar continuum is the sum of simple stellar populations (SSPs) convolved with the line-of-sight velocity distribution (LOSVD).

>>>>

Where $NUV-r$ is the color from SDSS's $k$-corrected absolute magnitude and $\mathcal{M}_i$ is the $i$-band magnitude from the NSA catalog. We further apply an \ewha\ $\ge$ 3\AA\ cut on galaxy spectra extracted from a 1.0~\reff\ aperture to ensure that all passive galaxies are removed from the sample \citep{Cid-Fernandes:2011}. Finally, we use the BPT diagnostic \citep{Baldwin:1981} to remove galaxies with possible AGN in their centers. Specifically, we use the emission line ratios, log([O~{\sc iii}]/H$\beta$) and log([N~{\sc ii}]/H$\alpha$), extracted from a 1.3~kpc aperture along with the maximum starburst line of \citet{Kewley:2001} as the demarcation between the star-forming branch and the AGN branch.

@@

In our previous work, \citetalias{Fu:2018}, using the 2168 unique galaxies from DR14 \citep{Abolfathi:2018}, we showed that $\sim$5.7\% of the MaNGA observations have at least one companion galaxy within the field of view of the IFU. In this work we use a refined pair identification process which is also expanded for the most recent internal data release, MPL-8.

@@

To select paired galaxies out of our object catalog, we inspect the spectra of each object. We use our own {\sc idl} based spectral fitting code, {\sc spfit}, to model the spectra from the MaNGA datacubes. {\sc spfit} simultaneously fits emission lines and the stellar continuum with the Levenberg-Marquardt nonlinear least-squares minimization algorithm \citepalias{Fu:2018}. Emission lines are parameterized as a Gauss-Hermite series and the stellar continuum is the sum of simple stellar populations (SSPs) convolved with the line-of-sight velocity distribution (LOSVD).
